### 2020-08-14 manuscript/manuscript.rmd
added global mds plots, did not knit

@@

  categories = 
    tibble(
      index = index,
      count = c(allocation_counts),
      x = fit$points[,1],
      y = fit$points[,2]
    ) %>%
    arrange(desc(count)) %>%
    mutate( cumsum = cumsum(count))

  categories %<>% mutate(rank = 1:nrow(categories))

gg_mds_phil = 
 pb_samples %>% 
  filter( matrix=="Philippe2009" ) %>% 
  filter( model=="Poisson+CAT" ) %>% 
  ggplot() +
  geom_point(aes(x=x, y=y, size=count), alpha=0.4 ) + 
  theme(legend.position="right")

gg_mds_whel = 
 pb_samples %>% 
  filter( matrix=="Whelan2017_strict" ) %>% 
  filter( model=="Poisson+CAT" ) %>% 
  ggplot() +
  geom_point(aes(x=x, y=y, size=count), alpha=0.4 ) + 
  theme(legend.position="right")

gg_rank_phil + ggtitle("(A) Philippe2009")

gg_rank_whel + ggtitle("(B) Whelan2017")

gg_mds_phil + ggtitle("(C) Philippe2017 Poisson+CAT")

gg_mds_phil + ggtitle("(D) Whelan2017 Poisson+CAT")

>>>>

```{r n_cat, fig.width=6, fig.height=12}

  categories = 
    tibble(
      index = index,
      count = c(allocation_counts),
      x = fit$points[,1],
      y = fit$points[,2]
    )

  if( ! all( categories$index == rownames(frequencies) ) ){
    stop("category indexes and frequency vector names do not match")
  }

  frequencies_tib = 
    as_tibble( frequencies )

  names( frequencies_tib ) = paste0( "aa.", names( frequencies_tib ) )

  categories %<>% 
    bind_cols( frequencies_tib ) %>%
    arrange(desc(count)) %>% 
    mutate( cumsum = cumsum(count)) %<>% 
    mutate(rank = 1:nrow(categories))

pb_frequencies = pb_samples %>% select( starts_with("aa.") ) %>% data.matrix()

fit = cmdscale( dist( pb_frequencies ) ,eig=TRUE, k=2)

pb_samples %<>% mutate( x_global = fit$points[,1], y_global = fit$points[,2] )

gg_mds_phil = 
 pb_samples %>% 
  filter( matrix=="Philippe2009" ) %>% 
  ggplot() +
  geom_point(aes(x=x_global, y=y_global, size=count, col=model), alpha=0.4 ) + 
  theme(legend.position="right")

gg_mds_whel = 
 pb_samples %>% 
  filter( matrix=="Whelan2017_strict" ) %>% 
  ggplot() +
  geom_point(aes(x=x_global, y=y_global, size=count, col=model), alpha=0.4 ) +  
  theme(legend.position="right")

gg_chain = 
ggarrange(
  gg_rank_phil, 
  gg_rank_whel, 
  gg_mds_phil, 
  gg_mds_whel, 
  ncol  = 2, 
  nrow = 2, 
  labels = c("A Philippe2009", "B Whelan2017", "C", "D"), 
  common.legend = TRUE
)

@@

gg_chain
